A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-09 project/PaperTemplate/paper.Rmd
Minor edit

```{r normal simulation}
run_sim_normal <- function(sim_reps) {
  # create function to return mean and sd of bootstrap replication
  boot.stat <- function(d, i) {
    d <- X[i]
    return (c(mean(d), sd(d)))
  }
  # initialize matrix to hold different bootstrap prop. 
  # for each sample size
  master <- matrix(nrow = num_sample_sizes, ncol = 5)
  # iterate through each sample size
  for(i in 1:num_sample_sizes) {
    # initialize vectors that hold if the CI contains true mean 
    # by iteration
    norm_contains <- rep(0, sim_reps)
    student_contains <- rep(0, sim_reps)
    percentile_contains <- rep(0, sim_reps)
    bca_contains <- rep(0, sim_reps)
    # 
    n <- sample_sizes[i]
    true_mean <- 0
    # perform 10,000 iterations of bootstraps
    for (j in 1:sim_reps) {
      X <- rnorm(n, 0, 1)
      values <- data.frame(X)
      # perform bootstrap and CIs
      results <- boot(data = values, statistic = boot.stat, R = boot_reps)
      ci <- boot.ci(results, conf = 0.95, 
                    type = c("norm", "perc", "bca", "stud"))
      # update vectors depending on if the CI contains true mean
      norm_contains[j] <- true_mean >= ci$normal[2] & 
        true_mean <= ci$normal[3]
      student_contains[j] <- true_mean >= ci$student[4] & 
        true_mean <= ci$student[5]
      percentile_contains[j] <- true_mean >= ci$percent[4] & 
        true_mean <= ci$percent[5]
      bca_contains[j] <- true_mean >= ci$bca[4] &
        true_mean <= ci$bca[5]
    }
    # add the sample size and average proportion to matrix
    master[i, 1] <- sample_sizes[i]
    master[i, 2] <- sum(norm_contains)/sim_reps
    master[i, 3] <- sum(student_contains)/sim_reps
    master[i, 4] <- sum(percentile_contains)/sim_reps
    master[i, 5] <- sum(bca_contains)/sim_reps
  }
  # some wrangling
  master_df <- as.data.frame(master) %>% 
      rename("Sample_Size" = V1, "Normal" = V2, "Studentized" = V3, 
             "Percentile" = V4, "BCa" = V5) 
  master_df
}
```

>>>>

```{r normal simulation}
run_sim_normal <- function(sim_reps) {
  # create function to return mean and sd of bootstrap replication
  boot.stat <- function(d, i) {
    d <- X[i]
    return (c(mean(d), sd(d)))
  }
  # initialize matrix to hold different bootstrap prop. 
  # for each sample size
  master <- matrix(nrow = num_sample_sizes, ncol = 5)
  # iterate through each sample size
  for(i in 1:num_sample_sizes) {
    # initialize vectors that hold if the CI contains true mean 
    # by iteration
    norm_contains <- rep(0, sim_reps)
    student_contains <- rep(0, sim_reps)
    percentile_contains <- rep(0, sim_reps)
    bca_contains <- rep(0, sim_reps)

    n <- sample_sizes[i]
    true_mean <- 0
    # perform 10,000 iterations of bootstraps
    for (j in 1:sim_reps) {
      X <- rnorm(n, 0, 1)
      values <- data.frame(X)
      # perform bootstrap and CIs
      results <- boot(data = values, statistic = boot.stat, R = boot_reps)
      ci <- boot.ci(results, conf = 0.95, 
                    type = c("norm", "perc", "bca", "stud"))
      # update vectors depending on if the CI contains true mean
      norm_contains[j] <- true_mean >= ci$normal[2] & 
        true_mean <= ci$normal[3]
      student_contains[j] <- true_mean >= ci$student[4] & 
        true_mean <= ci$student[5]
      percentile_contains[j] <- true_mean >= ci$percent[4] & 
        true_mean <= ci$percent[5]
      bca_contains[j] <- true_mean >= ci$bca[4] &
        true_mean <= ci$bca[5]
    }
    # add the sample size and average proportion to matrix
    master[i, 1] <- sample_sizes[i]
    master[i, 2] <- sum(norm_contains)/sim_reps
    master[i, 3] <- sum(student_contains)/sim_reps
    master[i, 4] <- sum(percentile_contains)/sim_reps
    master[i, 5] <- sum(bca_contains)/sim_reps
  }
  # some wrangling
  master_df <- as.data.frame(master) %>% 
      rename("Sample_Size" = V1, "Normal" = V2, "Studentized" = V3, 
             "Percentile" = V4, "BCa" = V5) 
  master_df
}
```
